---
title: "PSYC520-720 Reports pre-moderation report (2024-25)"
output: html_document
---

Authors: Andy Wills,  GPL 3, modified by Julien Besle

Load packages
```{r, message = FALSE}
library(tools)
library(tidyverse)
library(stringr)
```

Load data
```{r, message = FALSE}

base.folder <- "C:/Users/jbesle/OneDrive - University of Plymouth/Teaching/PSYC520/Module leader/Moderation 2024-25"
sample.folder <- "Reports sample marks 2025"

marks  <- NULL
markers  <- list.files(paste(base.folder,sample.folder,sep="/"))
for (this.marker in markers) {
    tmp  <- read_csv(paste(base.folder,sample.folder,this.marker,sep="/"))
    marker  <- file_path_sans_ext(this.marker)
    tmp  <- cbind(marker, tmp)
    marks  <- rbind(marks, tmp)
}

## Remove identical substring "Participant" at start of all identifiers
marks <- marks %>%
  mutate(Identifier = str_remove(Identifier, "^Participant "))

write_csv(marks, paste(base.folder,"mod-scores-2025.csv",sep="/"))
```

Check that we only have 4 reports with 4 unique identifiers
```{r}
unique(marks$Identifier)
```

## Calculate Mean score across all markers and reports
```{r}
grandmean  <- marks %>% summarise(mark = round(mean(Score),1)) |> pull(mark)
grandmean
```

So, across four reports, the mean score across 10 markers was 3.5, slightly higher than in 2022 and 2024

## Calculate overall score for each report (averaged across markers)
```{r}
marks %>% group_by(Identifier) %>% summarise(mark = round(mean(Score),1))
```

This year, I picked a narrower range than previous years, from 2.9 to 3.9.

The four reports are approx. equidistant in the range

## report marks by marker

Plot a graph of marks per marker:
```{r, message = FALSE}
# Calculate grades by marker and report
grades  <- marks %>% group_by(marker, Identifier) %>% summarise(mark = mean(Score))
# grades %>% pivot_wider(names_from = Identifier, values_from = mark)

samples <-levels(factor(grades$Identifier))
graph  <- grades %>%
  ggplot(aes(x=factor(Identifier, levels =samples),
             y=mark, group=marker)) +
  geom_line(aes(colour=marker)) +
  geom_point()

graph + facet_grid(marker ~ .)
```


Compare the rankings per marker:

```{r, message = FALSE}
ranks <- grades %>%
  group_by(marker) %>%
  mutate(rank_per_marker = rank(mark)) %>%
  select(-mark)
ranks %>% pivot_wider(names_from = Identifier, values_from = rank_per_marker)
```


All markers agreed on the ranking of the best report (rank = 4).

Most markers (12 out of 14) agree on the ranking of the worst report (rank = 1)

Almost as many markers (10 out of 14) agree on the ranking between 2 and 3


## Overall scores by marker

Distribution of overall score across markers:
```{r}
overall  <- marks %>% group_by(marker) %>% summarise(mark = round(mean(Score),1)) %>% arrange(mark)
hist(overall$mark)
```
Overall scores for each marker
```{r}
overall
```

Most markers were individually close to the group mean.

However the following were > +/- 0.3 away, suggesting over/under marking relative to peers:
```{r}
overall %>% filter(mark < grandmean-0.3) #Too harsh
overall %>% filter(mark > grandmean+0.3) #Too generous
```


## Which components have the most variance between markers?

Distribution of the SD across markers for all four reports and all 25 components (i.e. 100 different marks):

```{r, message = FALSE}
score.by.comp  <- marks %>% group_by(Description, Component, marker, Identifier) %>% summarize(Score = mean(Score))
score.sd  <- score.by.comp %>% group_by(Description, Component, Identifier) %>% summarise(SD = sd(Score)) %>% arrange(-SD)
hist(score.sd$SD)
```


Fairly Impressive, SD is below 1 for almost all component-Identifier pairs.
The top 6 SDs (>1) occurred for 2 reports (but different components).

Let's look at the components with the largest variability:
```{r}
tops <- score.sd %>% arrange(-SD)
head(tops)
```


The highest SD is for 'Sample sizes are justified through a power calculation' (component 8).

Let's look at the distribution of marks across markers for this component/report
```{r}
marks %>% filter(Component == 8) %>% filter(Identifier == "13472268") %>%
  select(marker, Score)
```

The next highest is for 'Discussion provides good considerations of the limitations of the current study' (component 20)
```{r}
marks %>% filter(Component == 20) %>% filter(Identifier == "13472270") %>%
  select(marker, Score)
```

